### 2021-11-26 appendix3/appendix.tex
update apendicies a,b,c

%!TEX root = ../thesis.tex
\chapter{Convergence without ephemeral phases\label{app:extend conv}}
For completeness, we include here proof of the convergence of the QBD-RAP scheme to the fluid queue without the need for the ephemeral initial states.

@@

\section{Technical results}
As in Appendix~\ref{app:tand}, we treat the cases of \(m=0\) and \(m\geq 1\) seperately. We start with the case \(m=0\). The following result is analgous to Lemma~\ref{lem: Dcoajc}, though the proof is somewhat more tedious.

@@

	Since \(|\psi|\leq F\) then 
	\begin{align}
		|d_1|&\leq \left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s \int_{x=0}^{\Delta}  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1)  \wrt x_1 \wrt x \wrt u\right|F.\label{eqn:  CVBNM}
	\end{align}
	From Property~\ref{properties: -2}, (\ref{eqn:  CVBNM}) is less than or equal to 
	\begin{align}
		\nonumber &\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs e} h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u\right|F
		\\\nonumber &\leq\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s  \int_{x_1=0}^\infty \bs k(u) {\bs e} h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u\right|F
		\\&=\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s  \int_{x_1=0}^\infty h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u\right|F\label{eqb:afsgh}
	\end{align}
	since \(\bs k(u)e^{\bs Sx_1}\bs e\) is decreasing in \(x_1\) and \(\bs k(u)\bs e=1\). Now, as \(h_{ij}^{--}(\lambda,x_1)\) is integrable with \(\int_{x_1=0}^\infty h_{ij}^{--}(\lambda, x_1)\wrt x_1\leq \widehat{ G}\), then (\ref{eqb:afsgh}) is less than or equal to
	\begin{align}
		\nonumber \left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s \wrt u\right|\widehat GF
		&=\mathbb P(Z>x_0+\Delta-\varepsilon\mid Z>x_0)\widehat G F
		\\&\leq\cfrac{\var{(Z)}/\varepsilon^2}{1-\var{(Z)}/\varepsilon^2} \widehat G F,\nonumber 
	\end{align}
	by Chebyshev's inequality, since \(x_0\in(2\varepsilon,\Delta-\varepsilon)\).

	Since \(|\psi(x)|\leq F\) and \(|h_{ij}^{--}(\lambda,x)|\leq G\), the third term in (\ref{eqn: llllL}) is less than or equal to 
	\begin{align}
		&\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u e^{\bs S x_1} {\bs v}(x) \wrt x \wrt x_1G F.\label{eqn: a big lola}
	\end{align} 
	Computing the integral over \(x_1\) in (\ref{eqn: a big lola}) gives
	\begin{align}
		& \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u (-\bs S)^{-1}{\bs v}(x) \wrt x G F\nonumber
		%
		\\&\leq  \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \wrt u \wrt x G_{\bs v} G F \nonumber
		%
		\\&= \int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s  \wrt u\Delta G_{\bs v} G F.\label{eqn: google the yes}
	\end{align}
	since, by property \ref{properties: 1}, \(\bs k(u)(-\bs S)^{-1}{\bs v}(x)\leq \bs k(u)\bs e G_{\bs v}=G_{\bs v}\). The bound (\ref{eqn: google the yes}) is equal to 
	\begin{align}
		\Delta \mathbb P(Z>x_0 + \Delta-\varepsilon) \wrt x G_{\bs v} G F
		\leq  \Delta \cfrac{\var(Z)}{(x_0-\varepsilon)^2} G_{\bs v} G F, \label{eqn: JjJ}
	\end{align}
	by Chebyshev's inequality.

	The first and second terms in (\ref{eqn: llllL}) are

	where the first equality holds from Property \ref{properties: 2}. The last term in (\ref{eqn: aKK}) is less than or equal to 
	\begin{align}
		\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su} \int_{x=0}^{\Delta} \bs s \left|r_{\bs v}(u,x)\right|\wrt x \wrt u F 
		%
		&\leq \int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su} \bs sR_{{\bs v},2} \wrt u F \nonumber 
		%
		\\&\leq R_{{\bs v},2} F, \label{eqn: HhHj}
	\end{align}
	by Property \ref{properties: 2}. The first two terms in (\ref{eqn: aKK}) are

	Since \(|\psi|\leq F\), the second and third terms in (\ref{eqn: LLkkK}) are less than or equal to 

@@

		&\int_{x=0}^{\Delta-\varepsilon}\int_{u=0}^{\min(\Delta-x_0-\varepsilon,\Delta-x-\varepsilon)} \bs k(x_0)e^{\bs Su}\bs s  \wrt u \wrt xGF \nonumber

>>>>

%!TEX root = ../thesis.tex
\chapter{Convergence without ephemeral phases\label{app:extend conv}}
For completeness, we include here results needed to prove the convergence of the convergence of the QBD-RAP scheme to the fluid queue without the need for the ephemeral initial states. Note that we only need to prove that the convergence up to, and at, the time of the first change of level of the QBD-RAP.

@@

\section{Technical results}
As we did in Appendix~\ref{app:tand}, we treat the cases of no changes, and \(m\geq 1\) changes, of phase from \(\calS_+\) to \(\calS_-\) and \(\calS_-\) to \(\calS_+\) seperately. We start with the \emph{no changes} case. The following result is analgous to Lemma~\ref{lem: Dcoajc}, though the proof is somewhat more tedious.

@@

	%% d1 %%
	Since \(|\psi|\leq F\) then 
	\begin{align}
		|d_1|&\leq \left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s \int_{x=0}^{\Delta}  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1)  \wrt x_1 \wrt x \wrt u\right|F.\label{eqn:  CVBNM}
	\end{align}
	From Property~\ref{properties: -2}, (\ref{eqn:  CVBNM}) is less than or equal to 
	\begin{align}
		\nonumber &\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs e} h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u\right|F
		\\\nonumber &\leq\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s  \int_{x_1=0}^\infty \bs k(u) {\bs e} h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u\right|F
		\\&=\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s  \int_{x_1=0}^\infty h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u\right|F\label{eqb:afsgh}
	\end{align}
	since \(\bs k(u)e^{\bs Sx_1}\bs e\) is decreasing in \(x_1\) and \(\bs k(u)\bs e=1\). Now, as \(h_{ij}^{--}(\lambda,x_1)\) is integrable with \(\int_{x_1=0}^\infty h_{ij}^{--}(\lambda, x_1)\wrt x_1\leq \widehat{ G}\), then (\ref{eqb:afsgh}) is less than or equal to
	\begin{align}
		\nonumber \left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s \wrt u\right|\widehat GF
		&=\mathbb P(Z>x_0+\Delta-\varepsilon\mid Z>x_0)\widehat G F
		\\&\leq\cfrac{\var{(Z)}/\varepsilon^2}{1-\var{(Z)}/\varepsilon^2} \widehat G F,\nonumber 
	\end{align}
	by Chebyshev's inequality, since \(x_0\in(2\varepsilon,\Delta-\varepsilon)\).

	%% d2 %% 
	Since \(|\psi(x)|\leq F\), then
	\begin{align}
		|d_2| &\leq \left| \int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s r_{\bs v}(u,x) \wrt u \wrt x \right|F
		%
		\\&\leq \left| \int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s  \wrt u \right|R_{\bs v,2}F
		%
		\\&\leq R_{\bs v,2}F,
	\end{align}
	where the first inequality holds from Property~\ref{properties: 2}, and the last inequality holds since \(\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s  \wrt u=\mathbb P(Z\in (x_0,x_0+\Delta-\varepsilon)\mid Z>x_0)\leq 1\).

	%% d3 %%
	Since \(|\psi(x)|\leq F\) and \(h_{ij}^{--}(\lambda,\Delta-u-x)\leq G\), then
	\begin{align}
		|d_3|&\leq \int_{u=0}^{\min(\Delta-x_0-\varepsilon,\Delta-x-\varepsilon)} \bs k(x_0)e^{\bs Su}\bs s \wrt u \Delta GF
		\\ &\leq \mathbb P(Z\leq\Delta-\varepsilon \mid Z>x_0) \wrt u \Delta GF\nonumber
		\\ &\leq \cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2} \Delta GF,\nonumber
	\end{align}
	where the last inequality holds from Chebyshev's inequality.

	%% d4 %%
	Similarly, since \(|\psi(x)|\leq F\) and \(h_{ij}^{--}(\lambda,\Delta-u-x)\leq G\), then
	\begin{align} 
		|d_4|&\leq \int_{x=0}^{x_0-2\varepsilon}\int_{u=\Delta-x_0+\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \wrt u \wrt x GF \nonumber
			\\& = \int_{x=0}^{x_0-2\varepsilon}\mathbb P(Z\in[\Delta+\varepsilon, \Delta-x-\varepsilon + x_0]\mid Z>x_0) \wrt x GF \nonumber
			\\& \leq \int_{x=0}^{x_0-2\varepsilon}\mathbb P(Z\in[\Delta+\varepsilon, \Delta-\varepsilon + x_0]\mid Z>x_0) \wrt x GF \nonumber
			\\& \leq \mathbb P(Z\in[\Delta+\varepsilon, \Delta-\varepsilon + x_0]\mid Z>x_0)  \Delta GF \nonumber
			\\& \leq \cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2} \Delta GF \nonumber
	\end{align}

	%% d5 %%
	Since \(|\psi(x)|\leq F\) and \(h_{ij}^{--}(\lambda,\Delta-u-x)\leq G\), then
	\begin{align} 
		|d_5|&\leq \int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \wrt u 1(x\in[x_0,x_0-2\varepsilon))\wrt xGF
		\\&\leq \int_{x=0}^{\Delta-\varepsilon} 1(x\in[x_0,x_0-2\varepsilon))\wrt xGF  \nonumber 
		\\&= 2\varepsilon GF,  \nonumber 
	\end{align}
	where the second inequality holds since \(\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \wrt u\leq 1\).

	%% d6 %% 
	Since \(|\psi(x)|\leq F\) and \(h_{ij}^{--}(\lambda,\Delta-u-x)\leq G\), then
	\begin{align}
		&|d_6| \leq \int_{x=x_0-2\varepsilon}^{x_0} \wrt x GF\nonumber 
		\\&= 2\varepsilon GF.
	\end{align}

	%% d7 %% 
	Since \(|\psi(x)|\leq F\) and \(h_{ij}^{--}(\lambda,\Delta-u-x)\leq G\) then
	\begin{align}
		|d_7|&\leq \mathbb P(|Z-\Delta|> \varepsilon\mid Z>x_0)\Delta GF
		\\&\leq \cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2}\Delta GF
	\end{align}

	Convergence follows after setting \(\varepsilon^{(p)}=\var(Z^{(p)})^{1/3}\) and observing that all the bounds \(|d_1|,\dots,|d_7|\) tend to 0, as does the bound on (\ref{eqn: the last one?}), given by \(2\varepsilon^{(p)}LF\Delta\), as \(p\to\infty\). 
\end{proof}

	Now we show bounds for certain Laplace transform expressions which arise when the QBD-RAP starts in phases in \(\calS_{+0}\cup\calS_{-0}\) and there is more than one change from \(\calS_+\) to \(\calS_-\) or \(\calS_-\) to \(\calS_+\) before the first change of level. These expressions have the form
	\begin{align}
		\int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) \bs D e^{\bs{S}x_1}\wrt x_1\bs D 
            	\left[\prod_{n=2}^{k-1}\int_{x_n=0}^\infty g_n(x_n) e^{\bs{S}x_n} \wrt x_n
		\bs D\right]
            	\int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n {\bs v}(x). \label{eqn: c30}
	\end{align}
	Here, we ultimately wish to show that (\ref{eqn: c30}) converges to \(g_{1,n}^*(\Delta-x_0,x)\). We do not do this directly, instead, we show that (\ref{eqn: c30}) is `close' to \(w_n(\Delta-x_0,x)\), then rely on the results from Appendix~\ref{app:tand} to get the desired convergence.

	Observe that by substituting the first matrix \(\bs D\) in the expression above for its integral expression, then (\ref{eqn: c30}) is equal to 
	\begin{align}
		&\int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs s\cfrac{\bs\alpha e^{\bs Sz_0}}{\bs\alpha e^{\bs Sz_0}\bs e} \wrt z_0 e^{\bs{S}x_1}\wrt x_1\bs D 
            	\left[\prod_{n=2}^{k-1}\int_{x_n=0}^\infty g_n(x_n) e^{\bs{S}x_n} \wrt x_n
		\bs D\right]
            	\\\nonumber&\quad\times\int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n {\bs v}(x) 
	%
		\\&=\bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0.\label{eqn: kd djv}
	\end{align}
	Intuitively, when the variance of \(Z\) is low, we expect that the integral in (\ref{eqn: kd djv}) above will be approximately equal to \(w_n(\Delta-x_0,x)\). Indeed, we proved in Lemma~\ref{lemma:bound} that this is the case for functions \(g\) satisfying the Assumptions~\ref{asu: g}. However, here we do not immediately have that \(w_n(x_0,x)\) is Lipschitz as we would need for it to satisfy Assumptions~\ref{asu: g}. Instead, we can show a Lipschitz-like condition in \(x_0\) for \(w_n(x_0,x)\), which suffices.

For later, observe that 
\begin{align}
	g^*_{2,n}(u_1,x) &= \int_{u_2=0}^{\Delta-u_1}g_2(\Delta - u_2 - u_1)\wrt u_1 \dots \nonumber 
         	\int_{u_{n-1}=0}^{\Delta-u_{n-2}} g_{n-1}(\Delta - u_{n-1} - u_{n-2}) \wrt u_{n-2}
       	\\&\qquad{}g_{n}(\Delta - x-u_{n-1})1(\Delta-x-u_{n-1}\geq0)\wrt u_{n-1} \nonumber
 %
 	\\&\leq G^{n-1}\int_{u_2=0}^{\Delta-u_1}\wrt u_1 \dots\nonumber
            	\int_{u_{n-1}=0}^{\Delta-u_{n-2}}  \wrt u_{n-1}
		\\&\leq G^{n-1}\Delta^{n-2}:=G^*_n.
\end{align}
Also, 
\begin{align}
	g^*_{2,n}(u_1,x) &= \int_{u_2=0}^{\Delta-u_1}g_2(\Delta - u_2 - u_1)\wrt u_1 \dots \nonumber 
         	\int_{u_{n-1}=0}^{\Delta-u_{n-2}} g_{n-1}(\Delta - u_{n-1} - u_{n-2}) \wrt u_{n-2}
       	\\&\qquad{}g_{n}(\Delta - x-u_{n-1})1(\Delta-x-u_{n-1}\geq0)\wrt u_{n-1} \nonumber
 %
 	\\&\leq G^{n-1}\int_{u_2=0}^{\Delta-u_1}\wrt u_1 \dots\nonumber
            	\int_{u_{n-1}=0}^{\Delta-u_{n-2}}  \wrt u_{n-1}
		\\&\leq G^{n-1}\Delta^{n-2}:=G^*_n.
\end{align}

% \begin{cor}\label{cor: ksjkd}
% 	Let \(g_1, g_2, \dots,\) be functions satisfying the Assumptions \ref{asu: g} and let \(\bs v(x)\) be a closing operator with the Properties \ref{properties: some props}, then,
% 	\begin{align}
% 		&\int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) e^{\bs{S}x_1}\wrt x_1\bs D 
%             	\left[\prod_{k=2}^{n-1}\int_{x_k=0}^\infty g_k(x_k) e^{\bs{S}x_k} \wrt x_k \bs D\right] \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \bs v(x) \nonumber 
% 		\\&\leq \cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e} \widehat{G}^{n-1}G(G_{\bs v}+\widehat G O(\var(Z)) \label{eqn :mmmm}
% 	\end{align}
% \end{cor}
% \begin{proof}
% 	By Corollary \ref{cor: amammme} 
% 	\begin{align}
% 		&\int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) e^{\bs{S}x_1}\wrt x_1\bs D 
%             	\left[\prod_{k=2}^{n-1}\int_{x_k=0}^\infty g_k(x_k) e^{\bs{S}x_k} \wrt x_k \bs D\right] \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \bs v(x)\nonumber
% 		\\&\leq \int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) e^{\bs{S}x_1}\wrt x_1\bs D 
% 		\left[\prod_{k=2}^{n-1}\int_{x_k=0}^\infty g_k(x_k) e^{\bs{S}x_k} \wrt x_k \bs D\right] \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n\bs w(x) \nonumber
% 		\\&\quad{} + O(\var(Z)). \label{eqn: LLaaNNab}
% 	\end{align}
% 	The first term of (\ref{eqn: LLaaNNab}) can be seen to be equivalent to \(\mathcal J_{1,n+1}(x_0,x_1),\) with \(g_1(x_1)=1\), and the integrability condition on \(g_1\) is not required to prove the bound. 
% \end{proof}

% \begin{cor}\label{cor: amammme}
% 	Let \(g_1, g_2, \dots,\) be functions satisfying the Assumptions \ref{asu: g} and let \({\bs v}(x)\) be a closing operator with the Properties \ref{properties: some props}, then,
% 	\begin{align}
% 		&\int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) e^{\bs{S}x_1}\wrt x_1\bs D 
%             	\left[\prod_{k=2}^{n-1}\int_{x_k=0}^\infty g_k(x_k) e^{\bs{S}x_k} \wrt x_k \bs D\right] \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \widetilde{\bs w}(x) \nonumber 
% 		% \\&= \int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) e^{\bs{S}x_1}\wrt x_1\bs D 
% 		% \left[\prod_{k=2}^{n-1}\int_{x_k=0}^\infty g_k(x_k) e^{\bs{S}x_k} \wrt x_k \bs D\right] \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n {\bs w}(x) \nonumber
% 		\\&= O(\var(Z)) \label{eqn :mmmm2}
% 	\end{align}
% \end{cor}
% \begin{proof}
% 	% First observe that 
% 	% \begin{align*} 
% 	% 	\int_{x_n=0}^\infty \bs\alpha e^{\bs S(u+x_n)}{\bs v}(x)\wrt x_n 
% 	% 	&=\int_{x_n=0}^\infty \bs\alpha e^{\bs S(u+x_n)} (\bs w(x)+\widetilde{\bs w}(x))\wrt x_n
% 	% 	\\&=\int_{x_n=0}^\infty \bs\alpha e^{\bs S(u+x_n)} \bs w(x)\wrt x_n + \bs\alpha e^{\bs S(u+x_n)} \widetilde{\bs w}(x))\wrt x_n
% 	% \end{align*}
% 	% and recall that Property \ref{properties: 0} states 
% 	% \begin{align}
% 	% 	\int_{x_n=0}^\infty \bs\alpha e^{\bs S(u+x_n)} \widetilde{\bs w}(x)\wrt x_n = \bs\alpha e^{\bs Su}(-\bs S)^{-1} \widetilde{\bs w}(x) = O(\var(Z)).
% 	% \end{align}

% 	Consider the left-hand side of (\ref{eqn :mmmm2}). Replacing the last \(\bs D\) matrix in (\ref{eqn :mmmm2}) by its integral definition, gives 
% 	\begin{align*}
% 		&\int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) e^{\bs{S}x_1}\wrt x_1
%             \left[\prod_{k=2}^{n-1}\bs D \int_{x_k=0}^\infty g_k(x_k) e^{\bs{S}x_k} \wrt x_k \right] \int_{u=0}^\infty e^{\bs S u}\bs s \cfrac{\bs \alpha e^{\bs S u}}{\bs \alpha e^{\bs S u} \bs e}\wrt u 
% 			\\&\qquad{}\int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \widetilde{\bs w}(x) 
% 		\\&=\bs k(x_0) \int_{u=0}^\infty \mathcal I_{1,n}(u) \cfrac{\bs \alpha e^{\bs S u}}{\bs \alpha e^{\bs S u} \bs e}\wrt u \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \widetilde{\bs w}(x) 
% 		\\&\leq \cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n-1} \int_{u=0}^\infty \bs \alpha e^{\bs{S}u}\bs e \cfrac{\bs \alpha e^{\bs S u}}{\bs \alpha e^{\bs S u} \bs e}\wrt u \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \widetilde{\bs w}(x) 
% 	\end{align*}
% 	by Lemma \ref{lem: lh bnd}. Integrating over \(u\) gives 
% 	\begin{align*}
% 		&\cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n-1} \bs \alpha (-\bs S)^{-1} \int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n \widetilde{\bs w}(x) 
% 		\\&\leq \cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n-1} \bs \alpha (-\bs S)^{-1} \int_{x_n=0}^\infty g_{n}(x_n) \wrt x_n \widetilde{\bs w}(x),
% 	\end{align*}
% 	by Property \ref{properties: -1}. Integrating over \(x_n\), gives
% 	\begin{align*}
% 		\cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n} \bs \alpha (-\bs S)^{-1} \widetilde{\bs w}(x) 
% 		&=\cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n}O(\var(Z)),
% 	\end{align*}
% 	by Property \ref{properties: 0}.
% \end{proof}

\begin{cor}\label{cor: ahjg}
	Let \(g_1,g_2,\dots,\) be functions satisfying Assumptions \ref{asu: g} and let \({\bs v}(x)\), \(x\in[0,\Delta)\), be a closing operator with Properties \ref{properties: some props}. For \(x_0,x\in\mathcal [0,\Delta)\), \(n\geq 2\), 
	\begin{align}
		&\left|\int_{x=0}\bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0 - w_n(\Delta - x_0,x) \right| \nonumber
		= r_8(n),
	\end{align}
	where 
	\begin{align*}
		|r_8(n)|&\leq  \left( 2|r_5(n)| + 2|r_6(n)| + 2(n-1)|r_4(n)| + \varepsilon G_n^{*}(G+L\Delta) \right) \\&\qquad{}+ 2\widehat G^{n-2}GG_{\bs v}\cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2}.
	\end{align*}
\end{cor}
\begin{proof}
	Now
	\begin{align}
		\nonumber&\left|\bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0 - w_n(\Delta - x_0,x) \right|
		\\\nonumber&= \left|\bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs s(w_n(z_0,x) - w_n(\Delta - x_0,x)) \wrt z_0\right|
		%
		\\\nonumber&\leq \bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs s  \left|w_n(z_0,x) - w_n(\Delta - x_0,x)\right| \wrt z_0
		%
		\\\nonumber&= \bs k(x_0) \int_{z_0=0}^{\Delta-\varepsilon-x_0} e^{\bs Sz_0}\bs s  \left|w_n(z_0,x) - w_n(\Delta - x_0,x)\right| \wrt z_0
		\\\nonumber&\qquad{}+\bs k(x_0) \int_{z_0=\Delta+\varepsilon-x_0}^\infty e^{\bs Sz_0}\bs s  \left|w_n(z_0,x) - w_n(\Delta - x_0,x)\right| \wrt z_0
		\\\label{eqn: KASJF}&\qquad{}+\bs k(x_0) \int_{z_0=\Delta-\varepsilon-x_0}^{\Delta+\varepsilon-x_0} e^{\bs Sz_0}\bs s  \left|w_n(z_0,x) - w_n(\Delta - x_0,x)\right| \wrt z_0.
		%
	\end{align}

		Using Equations~(\ref{eqn: in here}), (\ref{eqn: J bound}) and (\ref{eqn:FGHJSjjs sj}) we can claim
		\begin{align}
			|w_n(x_0,x)| &\leq \cfrac{1}{\bs \alpha e^{\bs{S} x_0}\bs e}G^2 \widehat G^{n-2}  
			\int_{u_k=0}^\infty \bs \alpha e^{\bs{S}u_k}\bs e \wrt u_k G_{\bs v} + \cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n}\widetilde G_{\bs v} \nonumber 
			\\& = \cfrac{1}{\bs \alpha e^{\bs{S} x_0}\bs e}G^2
			 \widehat G^{n-2} G_{\bs v} + \cfrac{1}{\bs \alpha e^{\bs{S}x_0}\bs e}G\widehat G^{n}\widetilde G_{\bs v} \nonumber 
			 \\&=:W_n
		\end{align}

		Therefore, the sum of the first two terms in (\ref{eqn: KASJF}) is less than or equal to 
		\begin{align}
		&2W_n\left(\int_{z_0=0}^{\Delta-\varepsilon-x_0}\bs k(x_0)e^{\bs S z_0} \bs s \wrt z_0+\int_{z_0=\Delta+\varepsilon-x_0}^\infty \bs k(x_0)e^{\bs S z_0} \bs s \wrt z_0\right)\nonumber 
		\\\nonumber &= 2W \cfrac{\mathbb P(|Z-\Delta|> \varepsilon)}{\mathbb P(Z> x_0)}
		\\&\leq 2W_n\cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2}
		\end{align}
		by Chebyshev's inequality. As for the last term in (\ref{eqn: KASJF}), we can use Corollary~\ref{cor: awrg} to bound the integrand so that the last term is less than or equal to 
		\begin{align}
		\nonumber&\bs k(x_0) \int_{z_0=\Delta-\varepsilon-x_0}^{\Delta+\varepsilon-x_0} e^{\bs Sz_0}\bs s \left( 2|r_5(n)| + 2|r_6(n)| + 2(n-1)|r_4(n)| + \varepsilon G^{n-1}\Delta^{n-2}(G+L\Delta) \right) \wrt z_0
		%
		\\\nonumber&\leq  \left( 2|r_5(n)| + 2|r_6(n)| + 2(n-1)|r_4(n)| + \varepsilon G^{n-1}\Delta^{n-2}(G+L\Delta) \right)
		\\&\quad{}+2W_n\cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2} ,
	\end{align}
	since \(\displaystyle \bs k(x_0) \int_{z_0=\Delta-\varepsilon-x_0}^{\Delta+\varepsilon-x_0} e^{\bs Sz_0}\bs s\wrt z_0\leq 1\). 
\end{proof}

\begin{cor} \label{cor: aaaaa}
	Let \(g_1,g_2,\dots,\) be functions satisfying Assumptions \ref{asu: g} and let \({\bs v}(x)\), \(x\in(0,\Delta)\), be a closing operator with Properties \ref{properties: some props}. For \(x_0,x\in(0,\Delta)\), \(n\geq 2\)
	\begin{align}
		&\left|\bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0- g_{1,n}^*(\Delta-x_0,x) \right| \nonumber
		\\&\leq |r_8(n)|+|r_5(n)|+|r_6(n)| + (n-1)|r_4(n)|,\label{eqn: KAFnn}
	\end{align}
	where 
	\begin{align}
		|r_8(n)|&\leq \left( 2|r_5(n)| + 2|r_6(n)| + 2(n-1)|r_4(n)| + \varepsilon G^{n-1}\Delta^{n-2}(G+L\Delta) \right) \\&\quad{} 
	+2\widehat G^{n-2}GG_{\bs v}\cfrac{\var(Z)/\varepsilon^2}{1-\var(Z)/\varepsilon^2}.
	\end{align}
\end{cor}
\begin{proof}
	Adding and subtracting \(w_n(\Delta-x_0,x)\) within the absolute value on the left-hand side of (\ref{eqn: KAFnn}) 
	\begin{align*}
		%&\Bigg| \int_{x_1=0}^\infty g_1(x_1) \bs k(x_0) \bs D e^{\bs{S}x_1}\wrt x_1\bs D 
%            	\left[\prod_{n=2}^{k-1}\int_{x_n=0}^\infty g_n(x_n) e^{\bs{S}x_n} \wrt x_n
%		\bs D\right]
%            	\int_{x_n=0}^\infty g_{n}(x_n) e^{\bs{S}x_n} \wrt x_n {\bs v}(x) \nonumber 
	%
%		\\&{}- g_{1,n}^*(\Delta - x_0,x) \Bigg| 
		&\left| \bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0 \nonumber 
	%
		 - w_n(\Delta - x_0,x) + w_n(\Delta - x_0,x) - g_{1,n}^*(\Delta - x_0,x) \right| 
		\\&\leq \left| \bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0 - w_n(\Delta - x_0,x)\right| + \left| w_n(\Delta - x_0,x) - g_{1,n}^*(\Delta - x_0,x) \right| 
	\end{align*}
	where the first absolute value is less than or equal to \(|r_8(n)|\) by Corollary~\ref{cor: ahjg} and the second absolute value is less than or equal to \(|r_5(n)|+|r_6(n)| + (n-1)|r_4(n)|\) by Corollary~\ref{cor: a cor}.
\end{proof}

\begin{cor}
	Let \(\psi\) be bounded and Lipschitz, let \(g_1,g_2,\dots,\) be functions satisfying Assumptions \ref{asu: g} and let \({\bs v}(x)\), \(x\in(0,\Delta)\), be a closing operator with Properties \ref{properties: some props}. For \(x_0,x\in(0,\Delta)\), \(n\geq 2\)

@@

		&\left| \int_{x\in[0,\Delta)}\bs k(x_0) \int_{z_0=0}^\infty e^{\bs Sz_0}\bs sw_n(z_0,x)\wrt z_0 \psi(x)\wrt x  
		- \int_{x\in[0,\Delta)} g_{1,n}^*(\Delta-x_0,x)\psi(x)\wrt x \right|\nonumber 
		\\&\leq \left(|r_8(n)|+|r_5(n)|+|r_6(n)| + (n-1)|r_4(n)|\right)F\Delta.\label{eqn: KAFnnmna2}
